\begin{center}  
\zihao{3}\textbf{Research and Implementation of Text Sentiment Analysis Based On Deep Learning}
\end{center}
%\vspace{0.5mm}
\begin{center}  
\zihao{-3}\textbf{ABSTRACT}
\end{center}
\vspace{2mm}
\zihao{-4}

Sentiment Analysis, SA, also called Opinoin/Review Mining, is aimed at analyzing the implied status, opinion, review of the speaker. It is widely used in many fields such as public opinion analysis, automated decision support, Ads recommendation. As a subtask, Text Sentiment Classification refers to detect the sentiment polarity of the input text. Due to the rich vocabulary, semantic ambiguity, complex grammar and irregular pragmatic phenomenon of natural language, Text Sentiment Classification remains a challenging task. In this paper, we concentrate on solving Text Sentiment Classification of the sentence level with deep learning method, however, we also implement a knowledge-based algorithm for study and contrast.


To solve this problem, we build three models: first, a knowledge based model using Stanford Parser; second, to get rid of the noise from complex grammar, we discard the global grammar feature and implement an model improved from C\&W model called Convolutional Neural Network on Phrase Level(CNNPL). In the last, because CNNPL can not handle with variable length sequence, in the meanwhile, recurrent neural network   such as Long Short-Term Memory(LSTM) can not extract phrase feature, we implement a model called Convolutional Neural Network with LSTM on Phrase Level(CNNLSTMPL) which combines CNNPL and LSTM cell. Both CNNPL and CNNLSTMPL achieve good results in the task SCDL, NLPCC 2014. Their accuracies are close to or slightly exceed the best results on the contest of NLPCC 2014. 


In the meanwhile, we prompt a process for handling sentiment classification using neural network, and then we analyze the important parameters of the process. Finally, we write a website to present those model by using Restful API.

\vspace{3mm}
\zihao{-4}{\bfseries KEY WORDS}\quad Deep Learning \quad Sentiment Analysis \quad Long Short-Term Memory \quad Convolutional neural network
